### 2016-03-01 introduction.tex
ready submit

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{onionring}
\caption{\scriptsize{The onion-ring model of repairs, showing all repairs for the center-most test case, and all other test cases repaired by those mutants.  Circles represent repairing mutants, and diamonds repaired test cases.  Diamond pattern symbolizes fault.  For the innermost ring of repairing mutant(s), all test cases are due to the same fault.  As rings expand to include more failures, the set of faults repaired grows (as does distance).}}
\label{fig:onion}
\end{figure}

Consider the structure of mutants repairing a failure due to some optimization.  If many mutants repair this failure, by turning off the optimization or a whole family of optimizations, some will likely repair failures due to different faults.  Repairs naturally produce an \emph{onion-ring} structure (Figure \ref{fig:onion}), where a failure is repaired by (1) some mutants that are very specific to its fault (the inner rings) and repair few failures, as well as other mutants (2) that repair more and more faults, up to a hypothetical mutant (3) that turns off all optimization in the compiler (e.g., by effectively adding {\tt -O0}), the outer ring of the onion.  This does not introduce confusion, because the more repairs two tests have in common, the more likely they are to be due to the same fault, and the more they disagree on, the less likely they are to be due to the same fault.  While especially intuitive as a consequence of disabling compiler optimizations, it seems likely this structure appears for repairs in many programs.  Disabling an optimization is a code change that (usually) does not cause any test case that only concerns semantics, not speed, to fail, but can avoid some failures.  For some oracles, many changes may fall into this classification:  for example, if the only oracle is to detect crashes, a fault can be avoided by aborting the program early.  Turning off a data-structure invariant checker is another possible false repair that might cover many different faults.  In all these cases, so long as there are other, more interesting and more specific ways to repair some faults, a distance metric can still distinguish faults effectively.

The idea of measuring the distance between failures (or other test cases) by their response to mutants is appealing.  The most important aspect of most applications of distances between executions is some aspect of causality \cite{LewisCause,ZellerBook}.  Since at least the work of Hume \cite{Hume1}, causality has been understood as answering some question of the form ``what would have made a difference in this effect?''  A program mutant is a very direct way to answer this question.  The problem with determining causes of events in computer programs is that, as in most problems of causality, too many things can make a difference, most of which are not interesting.  Program mutants are much more likely to be interesting causes for events in a program than changes to test cases, at least for fault identification and debugging purposes, because the practical use of knowing a cause is to change the cause and avoid or produce an effect.  Debugging by changing test cases is not useful; debugging by altering the program is precisely how we seek to use the causes we discover.  Using mutants as causes in order to measure similarity ``inverts'' the ideas of Lewis \cite{LewisCause,LewisCount}, where similarity determines causality.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{onionring}
\caption{\scriptsize{The onion-ring model of repairs, showing all repairs for the center-most test case, and all other test cases repaired by those mutants.  Rings represent repairing mutants, and diamonds repaired test cases.  Diamond pattern symbolizes fault.  For the innermost ring, all failures are due to the same fault.  As rings expand to include more failures, the set of faults grows (as does distance).}}
\vspace{-0.1in}
\label{fig:onion}
\end{figure}

Consider the structure of mutants repairing a failure due to some optimization.  If many mutants repair this failure, by turning off the optimization or a whole family of optimizations, some will likely repair failures due to different faults.  Repairs naturally produce an \emph{onion-ring} structure (Figure \ref{fig:onion}), where a failure is repaired by (1) some mutants that are very specific to its fault (the inner rings) and repair few failures, as well as other mutants (2) that repair more and more faults, up to a hypothetical mutant (3) that turns off all optimization in the compiler (e.g., by effectively adding {\tt -O0}), the outer ring of the onion.  This does not introduce confusion, because the more repairs two tests have in common, the more likely they are to be due to the same fault, and the more they disagree on, the less likely they are to be due to the same fault.  While especially intuitive as a consequence of disabling compiler optimizations, it seems likely this structure appears for repairs in many programs.  Disabling an optimization is a code change that (usually) does not cause any test case that only concerns semantics, not speed, to fail, but can avoid some failures.  For some oracles, many changes may fall into this classification:  for example, if the only oracle is to detect crashes, a fault can be avoided by aborting the program early.  Turning off a data-structure invariant checker is another possible false repair that might cover many different faults.  In all these cases, assuming more interesting and specific ways to repair faults exist, a distance metric can still work.

The idea of measuring the distance between failures (or other test cases) by their response to mutants is appealing.  The most important aspect of most applications of distances between executions is some aspect of causality \cite{LewisCause,ZellerBook}.  Since at least the work of Hume \cite{Hume1}, causality has been understood as answering some question of the form ``what would have made a difference in this effect?''  A program mutant is a very direct way to answer this question.  The problem with determining causes of events in computer programs is that, as in most problems of causality, too many things can make a difference, most of which are not interesting.  Program mutants are much more likely to be interesting causes for events in a program than changes to test cases, at least for fault identification and debugging purposes, because the practical use of knowing a cause is to change the cause and avoid or produce an effect.  Debugging by changing test cases is not useful; debugging by altering the program is precisely how we seek to use the causes we discover.  Using mutants as causes in order to measure similarity ``inverts'' the ideas of Lewis \cite{LewisCause,LewisCount}, where similarity determines causality.  One pleasant side-effect is that execution representation \cite{NearNeighbor,RepsSpectra} is not a difficulty for this kind of metric, since an execution is always represented as a set of correctness evaluations.
